---
title: "Data Tidying"
author: "Sandy De Groote"
date: "11/6/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning= F, message = F}
library(dplyr)
library(tidyr)
```

package_name::function_name(...)

obj <- stats::filter(x)

# REad and Clean DADTa
```{r}
catch_original <- read.csv(url("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/df35b.302.1", method = "libcurl"),
                          stringsAsFactors = FALSE)
head(catch_original)
```
Remove `all` column and `notes` column becaues we don't need them.

```{r}
catch_data <- catch_original %>% 
  # select (Region, Year, Chinook, Sockeye, Coho, Pink, Chum)
  select(-All, -notesRegCode) #this way tells what columns to get rid of

summary(catch_data)
```
## Fix Chinook Column

Use`mutate` to fix Chinook column

```{r}
catch_clean <- catch_data %>%
  mutate(Chinook = ifelse(Chinook == "I", 1, Chinook)) %>%
  mutate(Chinook = as.numeric(Chinook))
  
```
Finding the rows that got turned into NA

```{r}
i <- which(is.na(catch_clean$Chinook))
i
```
```{r}
catch_original[i, ]
```


# Reshape Data

```{r}
catch_long <- catch_clean %>%
  pivot_longer(cols = -c(Region, Year),
  names_to = "species",
  values_to = "count")
head(catch_long)
```


# Summarize Data

#Joins to region table